Dominance Regions for Imaginary $\bfg$-vectors

### 2021-07-25 dominance_regions.tex
Modified inequalities
Compatible pairs and greedy basis elements.

  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following six inequalities:
  \begin{align}
    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
  \end{align}
  Are any of these better forms?
  \begin{align}
    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
  \end{align}
  Another proposal (I also changed the order of the equations)
  \begin{align}
    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq \frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 
    \\
    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
    \\
    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
    \\
    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1
    \\
    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
  \end{align}

@@

>>>>

  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following six inequalities:
  \begin{align}
    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
  \end{align}
  Are any of these better forms?
  \begin{align}
    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
  \end{align}
  Another proposal (I also changed the order of the equations)
  \begin{align}
    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq \frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 
    \\
    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
    \\
    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
    \\
    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1
    \\
    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
  \end{align}
  Maybe this one:
  \begin{align}
    (b c-\sqrt{b c (b c-4)})(x-\lambda_1)+2b(y-\lambda_2) & \geq0
    \\
    (b c+\sqrt{b c (b c-4)})(x-\lambda_1)-2b(y-\lambda_2) & \geq (b c+\sqrt{b c (b c-4)})b\lambda_2 
    \\
    -(b c-\sqrt{b c (b c-4)})(x-\lambda_1)-2b(y-\lambda_2)& \geq 2bc\lambda_1+(b c+\sqrt{b c (b c-4)})b\lambda_2
    \\
    -2c(x-\lambda_1)-(b c-\sqrt{b c (b c-4)})(y-\lambda_2)& \geq0
    \\
    2c(x-\lambda_1)-(b c+\sqrt{b c (b c-4)})(y-\lambda_2) & \geq -(b c+\sqrt{b c (b c-4)})c\lambda_1
    \\
    2c(x-\lambda_1)+(b c-\sqrt{b c (b c-4)})(y-\lambda_2) & \geq -(b c+\sqrt{b c (b c-4)})c\lambda_1-2cb\lambda_2
  \end{align}

@@

  It will be convenient later to have explicit expressions for the greedy basis elements so we recall here the combinatorial construction of their Laurent expansions.
  For a $\bfg$-vector $\lambda\in\ZZ^2\setminus\ZZ_{\ge0}^2$, define the \emph{maximal Dyck path} $D_\lambda\subset\ZZ^2$ to be the lattice path with corner vertices $(0,0)$ and $(a_1,a_2):=\big([-\lambda_1+b\lambda_2]_+,[-\lambda_2]_+\big)$ which is maximal in the following sense:
  \begin{itemize}
    \item every lattice point of $D_\lambda$ lies below the line connecting the corner vertices;
    \item any lattice point above $D_\lambda$ lies above the line connecting the corner vertices.
  \end{itemize}
  For $\lambda\in\ZZ_{\ge0}^2$, we take $D_\lambda$ to be the empty path at $(0,0)$.

  We consider $D_\lambda$ to be the set of its edges ordered from $(0,0)$.
  Write $H_\lambda,V_\lambda\subset D_\lambda$ for the subsets of horizontal and vertical edges, respectively.
  According to the ordering of $D_\lambda$, we denote $H_\lambda=\{h_1,\ldots,h_{a_1}\}$ and $V_\lambda=\{v_1,\ldots,v_{a_2}\}$.
  For edges $e,e'\in D_\lambda$ with $e\le e'$, write $ee'\subset D_\lambda$ for the shortest subpath of $D_\lambda$ containing $e$ and $e'$.
  For edges $e,e'\in D_\lambda$ with $e'<e$, write $ee'\subset D_\lambda$ for the subset $ev_{a_2} \sqcup h_1e'$, which can be seen as the subpath traversing from the edge $e$ to the end of $D_\lambda$ and then continuing from the beginning of $D_\lambda$ to the edge $e'$.
  For any subset $S\subset D_\lambda$, write $|S|_H:=|S\cap H_\lambda|$ and $|S|_V:=|S\cap V_\lambda|$; in particular, for $e,e'\in D_\lambda$, write $|ee'|_H:=|ee'\cap H_\lambda|$ and $|ee'|_V:=|ee'\cap V_\lambda|$.
  \begin{definition}
    A subset $S\subset D_\lambda$ is said to be \emph{compatible} if: for every $h\in S\cap H_\lambda$ and $v\in S\cap V_\lambda$, there exists an edge $e\in hv$ so that one of the following conditions is satisfied:
    \begin{align*}
      e\ne v \quad \text{and} \quad |he|_V=c|he\cap S|_H;\\
      e\ne h \quad \text{and} \quad |ev|_H=b|ev\cap S|_V.
    \end{align*}
    Write $\cC_\lambda$ for the set of all compatible subsets $S\subset D_\lambda$.
  \end{definition}

  The \emph{greedy basis element} $x^{gr}_\lambda$ is then given by the following Laurent polynomial
  \begin{equation}
    \label{eq:greedy}
    x^{gr}_\lambda=x_1^{\lambda_1}x_2^{\lambda_2} \sum_{S\in \cC_\lambda} x_1^{b(|V_\lambda|-|S|_V)} x_2^{c|S|_H}.
  \end{equation}
